### 2022-03-10 sections/reviewer.tex
Update reviewer.tex

\begin{cvparagraph}

\begin{itemize}
\item{\small Varieties of Democracy Project, University of Gothenburg, Sweden, 2014, 2018-2020}
\item{\small Global Academic Reputation Survey, Clarivate Analytics, USA, 2020}
\item{\small Sectoral Commission for Research, Universidad de la Rep\'ublica, Uruguay, 2016, 2018}
\item{\small Times Higher Education World University Rankings, {\scshape Elsevier}, 
Netherlands, 2018-2019}
\item{\small Reviewer in {\scshape WoS} \& {\scshape Scopus} journals, since 2013}
\item{\small Reviewer in {\scshape SciELO} \& {\scshape Latindex} journals, since 2013}
\end{itemize}

\vspace{1mm}
\end{cvparagraph}

>>>>

\begin{publications}

\begin{itemize}
\item{\small Varieties of Democracy Project, University of Gothenburg, Sweden, 2014, 2018-2020}
\item{\small Global Academic Reputation Survey, Clarivate Analytics, USA, 2020}
\item{\small Sectoral Commission for Research, Universidad de la Rep\'ublica, Uruguay, 2016, 2018}
\item{\small Times Higher Education World University Rankings, {\scshape Elsevier}, 
Netherlands, 2018-2019, 2022}
\item{\small Reviewer in {\scshape WoS-ISI/SSCI/ESCI} \& {\scshape Scopus} journals, since 2013}
\item{\small Reviewer in {\scshape SciELO} \& {\scshape Latindex} journals, since 2013}
\end{itemize}

\vspace{1mm}
\end{publications}
